A mechanization of semi-simplicial and semi-cubical sets in the calculus of inductive constructions

### 2022-11-16 paper/paper.tex
paper: MAJ

% These are renewed in tables, but let's define them now for in-document
% typesetting
\newcommandx{\framep}[2][1,2]{\prim{frame}[][#1][#2][][]}
\newcommandx{\layer}[2][1,2]{\prim{layer}[][#1][#2][][]}
\newcommandx{\filler}[2][1,2]{\prim{filler}[][#1][#2][][]}
\newcommandx{\restrf}[3][1,2,3]{\restr{frame}[][#3][][#1][#2][][]}
\newcommandx{\fullframe}[1][1]{\prim{fullframe}[][#1][][][]}

@@

The figure on the left is $\framep[3][1]$, in the middle is $\framep[3][2]$, and on the right is $\framep[3][3]$. Further, $\layer[3][0]$ is shown in blue, $\layer[3][1]$ is shown in red, $\layer[3][2]$ is shown in green. In general, a $\layer[n][p]$ is a product of $\nu$ $\filler[n - 1][p]$. Then, a $\filler[n][p]$ is an $n$-dimensional object obtained by stretching a $(n - p)$-dimensional frame in $p$ directions. For instance, each of the two $\filler[2][0]$ of $\layer[3][0]$ is a filled blue square, each of the two $\filler[2][1]$ of $\layer[3][1]$ is the line shown in red, stretched into a square, and each of the two $\filler[2][2]$ of $\layer[3][2]$ is a point shown in green, stretched into a square. Note that a filler, which extends a frame with an element depending on it, shown as an element of $X_n$ below. As filler extends a frame, it also has layer components, but the layers are associated on the right that is opposite to the way they're associated in frames.

\begin{align*}
  \framep[n][p] & = \Sigma a_n : (\ldots (\Sigma \unitpoint : \unittype .\; \layer[n][0]) \ldots) .\; \layer[n][p] \\
  \filler[n][p] & = \Sigma l_p : \layer[n][p] . (\ldots (\Sigma l_n : \layer[n][n - 1] .\; X_n) \ldots)
\end{align*}

@@

\begin{align*}
  \framep[n][p](D) & = \Sigma a_n : (\ldots (\Sigma \unitpoint : \unittype .\; \layer[n][0]) \ldots) .\; \layer[n][p](D) \\
  \filler[n][p](D) & = \Sigma l_p : \layer[n][p] . (\ldots (\Sigma l_n : \layer[n][n - 1](D) .\; D.\tl) \ldots)
\end{align*}

So far, we haven't paid attention to the fact that each addition of a layer has to be glued onto the border of the previous layer. So, each $\layer[n][p]$ has to depend on $\layer[n][p - 1]$. We also need a way to characterize the border of a filler of a layer, and this is $\restrf[n][p][\epsilon]$, for all $\epsilon < \nu$. For instance, the left $\filler[2][1]$ needs to glue onto the left borders of the two blue boxes $c_{\textsf{front}}$ and $c_{\textsf{back}}$, extracted as $\restrf[2][1][L](D)(d_\textsf{front})$ and $\restrf[2][1][L](D)(d_\textsf{back})$, where $d_\textsf{front}$ and $d_\textsf{back}$ are the underlying fullframes in $c_\textsf{front}$ $c_\textsf{back}$.

@@

\begin{equation*}
  \filler[n+1][p] \defeq (\filler[n][p] \times \filler[n][p]) \times \filler[n+1][p+1]
\end{equation*}

@@

% Restriction for frame, layer, and filler
% Drop the unviverse letter
\renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
\newcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
\newcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{filler}[][#2][#3][#4][#5][#6][#7]}

>>>>

% These are renewed in tables, but let's define them now for in-document
% typesetting
\newcommandx{\framep}[2][1,2]{\prim{frame}[][#1][#2][][]}
\newcommandx{\layer}[2][1,2]{\prim{layer}[][#1][#2][][]}
\newcommandx{\filler}[2][1,2]{\prim{filler}[][#1][#2][][]}
\newcommandx{\restrf}[3][1,2,3]{\restr{frame}[][#3][][#1][#2][][]}
\newcommandx{\restrl}[3][1,2,3]{\restr{layer}[][#3][][#1][#2][][]}
\newcommandx{\restrc}[3][1,2,3]{\restr{filler}[][#3][][#1][#2][][]}
\newcommandx{\fullframe}[1][1]{\prim{fullframe}[][#1][][][]}

@@

The figure on the left is $\framep[3][1]$, in the middle is $\framep[3][2]$, and on the right is $\framep[3][3]$. Further, $\framep[3][1]$ is made of one layer, $\layer[3][0]$, shown in blue, $\framep[3][2]$ is made of one additional layer, $\layer[3][1]$, shown in red, $\framep[3][3]$ is made of one more layer, $\layer[3][2]$, shown in green. In general, a $\layer[n][p]$ is a product of $\nu$ $\filler[n - 1][p]$. Then, a $\filler[n][p]$ is an $n$-dimensional object obtained by stretching a $(n - p)$-dimensional frame in $p$ directions. For instance, each of the two $\filler[2][0]$ of $\layer[3][0]$ is a filled blue square, each of the two $\filler[2][1]$ of $\layer[3][1]$ is the line shown in red, stretched into a square, and each of the two $\filler[2][2]$ of $\layer[3][2]$ is a point shown in green, stretched into a square. Note that a filler, which extends a frame with an element depending on it, shown as an element of $X_n$ below. As filler extends a frame, it also has layer components, but the layers are associated on the right that is opposite to the way they're associated in frames.

\begin{align*}
  \framep[n][p] & \defeq \Sigma a_n : (\ldots (\Sigma \unitpoint : \unittype .\; \layer[n][0]) \ldots) .\; \layer[n][p] \\
  \filler[n][p] & \defeq \Sigma l_p : \layer[n][p] . (\ldots (\Sigma l_n : \layer[n][n - 1] .\; X_n) \ldots)
\end{align*}

@@

\begin{align*}
  \framep[n][p](D) & \defeq \Sigma a_n : (\ldots (\Sigma \unitpoint : \unittype .\; \layer[n][0](D)) \ldots) .\; \layer[n][p](D) \\
  \filler[n][p](D) & \defeq \Sigma l_p : \layer[n][p](D) . (\ldots (\Sigma l_n : \layer[n][n - 1](D) .\; D.\tl) \ldots)
\end{align*}

So far, we haven't paid attention to the fact that each addition of a layer has to be glued onto the border of the previous layer. So, each $\layer[n][p]$ has to depend on $\layer[n][p - 1]$. We also need a way to characterize the border of a filler of a layer, and this is $\restrf[n][p][\epsilon]$, for all $\epsilon < \nu$. For instance, each of the $\filler[2][1]$, shown as the red boxes, is laid on the borders of the blue boxes, and hence needs to depend on $\framep[3][1]$. The left and right borders of the two blue boxes are extracted as $\restrf[2][1][L](D)(d)$ and $\restrf[2][1][R](D)(d)$. We can then refine the previous equation by showing the dependencies on $d$.

\begin{align*}
  \framep[n][p](D)    & \defeq \Sigma d : (\ldots (\Sigma \unitpoint : \unittype .\; \layer[n][0](D)(\unitpoint)) \ldots) .\; \layer[n][p](D)(d)                              \\
  \filler[n][p](D)(d) & \defeq \Sigma l_p : \layer[n][p](D)(d) . (\ldots (\Sigma l_n : \layer[n][n - 1](D)(d, l_p, \ldots, l_{n - 1}) .\; D.\tl(d, l_p, \ldots, l_n)) \ldots) \\
  \text{where}\;      & (d, l_p, \ldots, l_q) \text{ abbreviates } ((\ldots(d, l_p), \ldots), l_q)
\end{align*}

Let us recall that a layer is made of two fillers. This can now be made precise as illustrated below.

\begin{align*}
  \layer[n][p](D)(d) & \defeq \filler[n-1][p](D.\hd)(\restrf[n][p][L](d)) \times \filler[n-1][p](D.\hd)(\restrf[n][p][R](d))
\end{align*}

We now define $\restrf[n][p][\epsilon]$ by recursion on the structure of a frame, which necessitates definitions of $\restrl[n][p][\epsilon]$ and $\restrc[n][p][\epsilon]$.

@@

\begin{align*}
  \filler[n+1][p] & \defeq (\filler[n][p] \times \filler[n][p]) \times \filler[n+1][p+1]
\end{align*}

@@

% Restriction for frame, layer, and filler
% Drop the unviverse letter
\renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
\renewcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
\renewcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{filler}[][#2][#3][#4][#5][#6][#7]}
